Crossing Origins by Crossing Formats

### 2012-12-03 main.tex
related work

First steps in exploiting the formats in the context of the web have
been by researchers. Two noteworthy examples are GIFAR~\cite{XXX} and
cross-origin CSS attacks~\cite{YYY} (Section~\ref{sec:related}
discusses further realted work). 
%
GIFAR is based on polyglots that combine the GIF and JAR (Java
archive) formats. The former is used as benign and the latter as
malicious to bypass SOP.
%
Cross-origin CSS attacks inject fragments of CSS code into an existing
web page to extract information from the existing web page.
%
The paper is the first to perform a systematic study of polyglot
attacks.
We characterize of what constitutes a dangerous format in the web setting and
identify particularly dangerous formats, with PDF as the prime example. We
demonstrate that polyglot-based attacks on the web open up for insecure
communication across Internet origins. We perform a systematic study of
PDF-based injection and content smuggling attacks.

@@

@@

Previous work documents instances of polyglot attacks based on syntax injection.
Huang et al.~\cite{Huang+:CCS10} describe a cross-origin \emph{cascading style-sheet} (CSS) attack. This 
attack injects fragments of CSS syntax in a HTML 
document, thereby making it a HTML/CSS polyglot. The error-tolerant parsing of 
style sheets allow the polyglot to parsed as valid CSS. The capabilities of CSS 
provide trivial cross-origin leakage. The paper proposes a defense technique which has been
adopted by all major browsers, which implies that the attacks outlined in the paper are now ineffective.
Instead,
Section
\ref{sec:vuln} will show practical attacks based on other formats.

@@

The Gifar attack is a polyglot attack based on content smuggling. In this attack 
a benign GIF-image and a malicious JAR-file is combined to create a GIF/JAR 
polyglot. By submitting the combined GIFAR to a service, the attacker can 
execute a Java applet under the origin of the targeted service. The Java runtime 
has been updated to prevent this kind of abuse.
Instead,
Section
\ref{sec:vuln} will show practical attacks based on other formats.

@@

@@

\subsection{PDF-based polyglots}
Several design choices in the PDF specification make the format particularly 
suitable for making polyglots. One such design choice is the error tolerant 
parser. This is in part motivated it being a container format, of which the 
implication is that a PDF file can, by design, contain foreign syntax that 
could interfere with the syntax of the file. Another motivation is that PDF 
files are designed to be both forward- and backward-compatible. Readers 
implementing an older version of the specification do not recognize new 
features and behave as if they were not present in the file. 
%
The implementation notes of the specification describes some exceptions to the
requirements of the specification, such as the header can occur 
anywhere within the first 1024 bytes of the file. This flexibility gives plenty of room for 
combining with syntax of another format.
%
The specification declares many components to be required in a
PDF file, but as can be seen in Section~\ref{sec:format}, in practice several 
components can be omitted. The code in Listing~\ref{lst:minimal-pdf} shows the 
minimal syntax required for a malformed, but valid PDF file.\todo{cite Julia Wolf?}
%incrementally 
%updated by appending updated versions of existing objects to 
%the end of the file. In fact, 
%and formats. This and the fact that it is designed to be robust against errors,
%provides us with a format that is powerful, flexible and ideal for creating
%malicious polyglots.

@@

@@

Barth et al.~\cite{Barth+:SP09}

Sundareswaran and Squicciarini~\cite{Sundareswaran:Squicciarini:CEAS10}

Wolf~ OMG WTF PDF talk at CCC in 2010.

PDFAR

@@

%1-2 pages 
\bibliographystyle{plain}
\bibliography{literature}

\newpage
\section*{Todo}
Test page \url{http://internot.noads.biz} with Billy's and Jonas' anonymized demos?

\end{document}

>>>>

First steps in exploiting the formats in the context of the web have
been by researchers. Two noteworthy examples are GIFAR~\cite{Brandis:GIFAR} and
cross-origin CSS attacks~\cite{Huang+:CCS10} (Section~\ref{sec:related}
discusses further related work). 
%
GIFAR is based on polyglots that combine the GIF and JAR (Java
archive) formats. The former is used as benign and the latter as
malicious to bypass SOP.
%
Cross-origin CSS attacks inject fragments of CSS code into an existing
web page to extract information from the existing web page.
%
The paper is the first to perform a systematic study of polyglot
attacks.
We characterize of what constitutes a dangerous format in the web setting and
identify particularly dangerous formats, with PDF as the prime example. We
demonstrate that polyglot-based attacks on the web open up for insecure
communication across Internet origins. We perform a systematic study of
PDF-based injection and content smuggling attacks.

@@

\paragraph{Syntax injection}

@@

Previous work documents instances of polyglot attacks based on syntax injection.
Huang et al.~\cite{Huang+:CCS10} describe a cross-origin \emph{cascading style-sheet} (CSS) attack. This 
attack injects fragments of CSS syntax in a HTML 
document, thereby making it a HTML/CSS polyglot. The error-tolerant parsing of 
style sheets allow the polyglot to parsed as valid CSS. The capabilities of CSS 
provide trivial cross-origin leakage. The paper proposes a defense technique which has been
adopted by all major browsers, which implies that the attacks outlined in their paper are now ineffective.
Instead,
Section
\ref{sec:vuln} will show practical attacks based on other formats.

@@

The GIFAR attack is a polyglot attack based on content smuggling. In this attack 
a benign GIF-image and a malicious JAR-file is combined to create a GIF/JAR 
polyglot. By submitting the combined GIFAR to a service, the attacker can 
execute a Java applet under the origin of the targeted service. The Java runtime 
has been updated to prevent this kind of abuse.
Instead,
Section
\ref{sec:vuln} will show practical attacks based on other formats.

@@

The reader is invited to visit the test page~\cite{Test:Page:12} for
practical demonstration of the concepts from this section.

@@

\subsection{PDF-based polyglots}
Several design choices in the PDF specification make the format particularly 
suitable for making polyglots. One such design choice is the error tolerant 
parser. This is in part motivated it being a container format, of which the 
implication is that a PDF file can, by design, contain foreign syntax that 
could interfere with the syntax of the file. Another motivation is that PDF 
files are designed to be both forward- and backward-compatible. Readers 
implementing an older version of the specification do not recognize new 
features and behave as if they were not present in the file. 
%
The implementation notes of the specification describes some exceptions to the
requirements of the specification, such as the header can occur 
anywhere within the first 1024 bytes of the file. This flexibility gives plenty of room for 
combining with syntax of another format.
%
The specification declares many components to be required in a
PDF file, but as can be seen in Section~\ref{sec:format}, in practice several 
components can be omitted~\cite{Wolf:CCC10}. The code in Listing~\ref{lst:minimal-pdf} shows the 
minimal syntax required for a malformed, but valid PDF file.
%incrementally 
%updated by appending updated versions of existing objects to 
%the end of the file. In fact, 
%and formats. This and the fact that it is designed to be robust against errors,
%provides us with a format that is powerful, flexible and ideal for creating
%malicious polyglots.

@@

As discussed in Section~\ref{sec:cross}, 
GIFAR~\cite{Brandis:GIFAR} is based on polyglots that combine the GIF and JAR (Java
archive) formats. The former is used as benign and the latter as
malicious to bypass SOP. The Java virtual machine vendors have since
then mitigated these attacks by patching the virtual machine to be
more conservative on the format of the executed files.

PDFAR~\cite{PDFAR:09} polyglots combine the PDF and JAR formats, where
PDF serves as benign and JAR serves as malicious. Such a polyglot is
possible due to the liberty of the requirements on the headers of PDF
files. Mitigation against GIFAR attacks in the Java virtual machine
effectively applies to PDFAR attacks.

@@

Barth et al.~\cite{Barth+:SP09} focus on security implications of
content sniffing by browsers. They present content-sniffing XSS
attacks by crossbreeding HTML with other formats like postscript. They
show attacks on real systems like HotCRP, where an uploaded conference
paper in the postscript format is interpreted as malicious HTML by the
browser. They also propose a content-sniffing algorithm that does not
suffer that helps defending against these class of attacks while
maintaining compatibility.

Sundareswaran and
Squicciarini~\cite{Sundareswaran:Squicciarini:CEAS10,Sundareswaran:Squicciarini:SecureComm10} discuss image
repurposing for GIFAR attacks. They present the AntiGifar tool for
client-side protection. AntiGifar models the benign behavior of a user
by a control-flow graph and detects possible anomalies when the
interactions of the user and browser with the web site deviate from
the control-flow model.

As mentioned in Section~\ref{sec:cross}, Huang et
al.~\cite{Huang+:CCS10} study an HTML/CSS attack. This attack injects
fragments of CSS syntax in a HTML document, thereby making it a
HTML/CSS polyglot. The error-tolerant parsing of style sheets allow
the polyglot to parsed as valid CSS. The capabilities of CSS provide
trivial cross-origin leakage. As discussed earlier, the paper's
defense technique has been adopted by all major browsers, which
implies that the attacks outlined in their paper are now ineffective.

Wolf's OMG WTF PDF presentation~\cite{Wolf:CCC10} is one of the main
starting points for this work. The presentation explores the liberty
of the PDF format. In addition, it highlights that PDF interpreters
often disregard the specification demands. This particularly
relevant as it allows crossbreeding PDF with such
formats as ZIP and EXE.

Heiderich et al.~\cite{Heiderich+:CCS11} explore the Scalable Vector
Graphics (SVG) format. They discover attacks that allow SVG files,
embedded via the \emph{img} tag, to run arbitrary JavaScript. 
One of the
attack vectors involves an SVG/HTML polyglot
that behaves differently depending on the context in which it is
accessed. When included in the \emph{img} tag, the file is interpreted as SVG,
whereas when it is accessed directly it is interpreted as malicious HTML.

@@

%1-2 pages 
\bibliographystyle{plain}
\bibliography{literature}
\end{document}
